Quantifying and partitioning uncertainties in retrievals of plant traits from imaging spectroscopy data

### 2020-12-03 manuscript/manuscript.tex
Minor formatting fixes

\begin{table}
\caption{\label{tab:combinations} Factorial combination of inputs}
\centering
\begin{tabular}{p{0.2\linewidth}lp{0.4\linewidth}p{0.3\linewidth}}
  \hline
  Variable & Size & Values & Comments \\
  \hline
  Atmosphere & 10 & \emph{See Table~\ref{tab:atmospheres}} & \\ 
  \hline
  Constellation inter-calibration scale & 3 & 0, 16, 32 & & \\
  Constellation atmospheric noise (\%) & 4 & 0, 1, 5, 10 & & \\
  Constellation angular noise (\%) & 4 & 0, 1, 5, 10 & & \\
  \hline
  Local time (24H) & 10 & 9:30, 10:00, 10:15, 10:30, 10:45, 11, 12, 13:30, 15:00 & Spaced over the day, with denser sampling around typical ``A-train'' satellite overpass around 10:30AM \\
  Date & 7 & March 20, May 20, June 20, July 20, August 20, September 22, December 21 & Northern hemisphere equinoxes and solstices, as well as denser sampling in summer (when traits are typically mapped) \\
  Sensor zenith (degrees) & 6 & 0, 12.5, 25, 37.5, 50, 75  & \\
  Sensor relative azimuth (degrees) & 5 & 0, 30, 60, 90, 180 & \\
  \hline
  Total grid size & \multicolumn{3}{l}{21,000} & & \\
  \hline
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{\label{tab:combinations} Factorial combination of inputs}
\centering
\begin{tabular}{p{0.2\linewidth}lp{0.4\linewidth}p{0.3\linewidth}}
  \hline
  Variable & Size & Values & Comments \\
  \hline
  Atmosphere & 10 & \emph{See Table~\ref{tab:atmospheres}} & \\ 
  Constellation inter-calibration scale & 3 & 0, 16, 32 & \\
  Constellation atmospheric noise (\%) & 4 & 0, 1, 5, 10 & \\
  Constellation angular noise (\%) & 4 & 0, 1, 5, 10 & \\
  Local time (24H) & 10 & 9:30, 10:00, 10:15, 10:30, 10:45, 11, 12, 13:30, 15:00 & Spaced over the day, with denser sampling around typical ``A-train'' satellite overpass around 10:30AM \\
  Date & 7 & March 20, May 20, June 20, July 20, August 20, September 22, December 21 & Northern hemisphere equinoxes and solstices, as well as denser sampling in summer (when traits are typically mapped) \\
  Sensor zenith (degrees) & 6 & 0, 12.5, 25, 37.5, 50, 75  & \\
  Sensor relative azimuth (degrees) & 5 & 0, 30, 60, 90, 180 & \\
  \hline
  Total grid size & \multicolumn{3}{l}{21,000} \\
  \hline
\end{tabular}
\end{table}
